Analysis paper

### 2021-06-03 analysis/analysis.Rmd
add ensemble plots

@@

models_plot <- c("Crowd forecast", "Hub-ensemble-with-crowd", "Hub-ensemble")

@@

comparison_ensembles(models_plot)

>>>>

#### Number of members in the ensemble
```{r}
ens <- ensemble_members %>%
  melt(id.vars = c("Date", "model"))

epinow2_included <- ens[model == "epiforecasts-EpiNow2", "epinow" := value]
crowd_included <- ens[model == "epiforecasts-EpiExpert", "crowd" := value]

p <- ens[, .(value = sum(value), 
             epinow = sum(epinow, na.rm = TRUE), 
             crowd = sum(crowd, na.rm = TRUE)), by = c("variable", "Date")] %>%
  ggplot(aes(y = value, x = Date, color = variable)) + 
  geom_point()

ggsave(here("analysis", "plots", "ensemble-members.png"), 
       plot = p)

### Comparing ensembles with and without a model

@@

@@

models_plot <- c("Crowd forecast", "Hub-ensemble-with-crowd", "Hub-ensemble")
p <- comparison_ensembles(models_plot)
ggsave(here("analysis", "plots", "ensemble-with-and-without-crowd.png"), 
       plot = p)

models_plot <- c("Renewal", "Hub-ensemble-with-renewal", "Hub-ensemble")
p <- comparison_ensembles(models_plot)
ggsave(here("analysis", "plots", "ensemble-with-and-without-renewal.png"), 
       plot = p)

models_plot <- c("Renewal", "Crowd forecast", "Hub-ensemble-all", "Hub-ensemble")
p <- comparison_ensembles(models_plot)
ggsave(here("analysis", "plots", "ensemble-with-and-without-both.png"), 
       plot = p)
